
\experienceTitle{Giorgio}{Jan 2023--Present}{CTO \& Co-Fouder}{São Paulo, SP}

In this phase, we made a shift in our venture's focus, transitioning towards the advancement of intelligent chatbots.\\
This \textbf{scalable, customizable} product holds potential for diverse applications currently being used for wine retailing and customer services.\\
\textbf{Led a four-member team} in developing an advanced WhatsApp-based chatbot, resulting in:
\begin{itemize}
  \item Architected a \textbf{modular, customizable and scalable product}, designing a flexible system that could adapt to varying requirements and future expansion.
  \item Orchestrated the deployment and continuous maintenance of \textbf{AWS (ECS) to host Docker containers}, ensuring a reliable and efficient infrastructure for operation.
  \item Utilized \textbf{Memcache} to optimize response times, ensuring smooth and \textbf{responsive user interactions}.
  \item Enhanced user engagement by seamlessly \textbf{integrating the OpenAI API}, delivering natural and contextually relevant interactions.
  \item Developed a secure SSL-integrated webhook for the \textbf{WhatsApp Business API, ensuring data security and privacy} while enabling seamless communication.
  \item Streamlined user engagement and data management by skillfully \textbf{integrating HubSpot}, serving as a comprehensive \textbf{database and CRM} solution.
\end{itemize}
% \vspace{0.6em}

\experienceTitle{Giorgio}{Oct 2021-- Jan 2023}{Software Engineer \& Co-Fouder}{São Paulo, SP}

During this timeframe, we accomplished several significant milestones. We successfully crafted an application for optimal restaurant selection, catering to diverse experiences within São Paulo City. Additionally, we engineered a recommendation system designed to propose ideal travel destinations tailored to individual user preferences.\\
Our application garnered substantial traction, boasting a user base of \textbf{more than 300 recurring users and 1000 active weekly users}. These achievements paved the way for securing a noteworthy \textbf{R\$100k investment, valuing our venture at R\$1000k}.\\
\textbf{Led a team of two} in the development achieving:
\begin{itemize}
  \item Developed a \textbf{Docker} server with \textbf{Python (Flask), using AWS ECS}.
  \item Implemented \textbf{AWS S3 (with Load Balancers)} to manage extensive media content.
  \item Streamlined the development process with \textbf{GitHub actions (CI/CD)} enabling continuous development practices.
  \item Maintained data operations with \textbf{Google Firestore}, ensuring low latency and efficient data handling. 
  \item Migrated and sustained services from Google to AWS platforms \textbf{(Lambda, S3, load balancers)}, resulting in an average \textbf{monthly cost reduction of 80\% on cloud expenses}.
  \item Integrated with various Google products like microservices, databases, storage, and cloud distribution systems \textbf{(Cloud Functions, Firestore, Cloud Storage, Cloud CDN)}.
  \item Collected and managed data to generate \textbf{Google Data Studio} dashboards, enabling the monitoring of performance metrics for the developed application.
\end{itemize}
